General constraints on magic state protocols from the statistical mechanics of \\Wigner negativity

### 2021-06-16 magic_paper.tex
minor changes

\begin{abstract}
Magic states are key ingredients in schemes to realise universal fault-tolerant quantum computation.
Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms. Here we develop a statistical mechanical framework in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits. While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds. These upper bounds are shown to be tighter than other bounds, such from mana and thauma, and moreover incorporate hardware physics, such as temperature dependence and physical Hamiltonians. We also show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values. We show that the mana of a magic state is the measure of divergence of these Renyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting. This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
\end{abstract}

@@

Consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$. On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, acting on the basis states as follows,
\begin{align}
    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
\end{align}
Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$. From these we can construct a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system. Given a point $\bmx \coloneqq (x, p)$ we define a displacement operator, 
\begin{equation}\label{eq:ddef}
    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ 
\end{equation}
where the phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity. We assume going forward that $d$ is an odd prime, however the case $d=2$ can also be handled, but with some additional technical caveats~\cite{Appleby_2005}. For a composite system with composite dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
\begin{equation}\label{eq:composited}
    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
\end{equation}
where now we have
\begin{align*}
	\bmx \coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d,
\end{align*}
to denote the phase space point for the composite system. 
For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\x \in \mathbb{Z}_d^{2n}$.

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{figs/test/R_vs_A.pdf}
    \caption{\textbf{Variation of distillation bounds with Hamiltonian.} We consider $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
    }
    \label{fig:rvsa}
\end{figure}

@@

However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
\begin{equation}
D_\infty (\p ||\r) = \log \max_i \frac{p_i}{r_i}.
\end{equation}
It is clear that this does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning, and in~\cref{app:lcst_technical}, we show that this divergence has the following properties that are derived via relative majorization.
\begin{theorem}\label{thm:Dinfty} 
	Let $\tau$ be in the interior of $\F$. Then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
\begin{enumerate}
\item $D_\infty(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\infty(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
\item $D_\infty(W_{\rho^{\otimes 2n}}|| W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} ||W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
\item $D_\infty(W_\rho || W_\tau) \geq D_\infty(W_{\E(\rho)} || W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
\end{enumerate}
\end{theorem}

@@

The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges in a well-defined way. We can write the divergence of the entropy as 
\begin{equation}
H_{1-\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}
\end{equation} 
with $\epsilon \rightarrow 0^+$ through a sequence of rational values. We now recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana:
\begin{equation}
\M(\rho) = \lim_{\epsilon \rightarrow 0^+} \epsilon H_{1-\epsilon}(W_\rho).
\end{equation}
Therefore, up to a factor $2\pi i$, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies \emph{the divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(W_\rho)$.

We also note that the Renyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.  For this, the Renyi parameter becomes a temperature term $\alpha = \frac{T_0}{T}$ where $T_0$ is a reference temperature and derivatives are considered via the limit $T \rightarrow T_0$. Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$. We can therefore speculate whether the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition [\ddd{cite}]. However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [\ddd{cite}].

Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for Renyi divergences of Wigner distributions.
The $\alpha$--Renyi divergence $D_\alpha(\p||\r)$ is defined as
\begin{equation}
	D_\alpha(\p || \r) := \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
\end{equation}
where $\p$ can be a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ can take the same values as for $H_\alpha$.
In~\cref{app:lcst_technical}, we also show that the divergence satisfies the following.

\begin{theorem}\label{thm:Da_props} 
	Let $\tau$ be in the interior of $\F$. 
	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
\begin{enumerate}
\item $D_\alpha(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\alpha(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
\item $D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho || W_\tau)$ for any $n \in \mathbb{N}$.
\item $D_\alpha(W_\rho || W_\tau) \geq D_\alpha (W_{\E(\rho)} || W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
\end{enumerate}
\end{theorem}

@@

	We have the following family of upper bounds on the magic distillation rate $R := m/n$,
	\begin{equation}
		R \leq \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution. 
\end{theorem}
For magic protocols that preserve unital maps, the above bound reduces to the simpler form
\begin{equation}
	R \leq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
\end{equation}
In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
\begin{equation}
	R \leq \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
\end{equation}
The upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
%
%\begin{figure}[t!]
%    \centering
%    \subfigure[][]{%
%    \label{fig:Ra}%
%    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
%    \subfigure[][]{%
%    \label{fig:RaDiff}%
%    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
%    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation for unital protocols
%    \nick{Can compare thauma and mana for other magic states now more easily}}
%    \label{fig:rate_a_contour}
%\end{figure}

@@

We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system. Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit. It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}]. This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply. That said, for special states such as the Strange state, the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible. In~\cref{app:lcsu_technical} and~\cref{app:lcst_technical} we give additional results that may be of use for later work.

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{figs/test/H_vs_eps_a.pdf}
    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $H_\alpha$ is increasing in $\alpha$ and $\epsilon$. First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$. Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ that implies $6^\alpha - 2^{\alpha} = 8$, with the approximate solution $\alpha \approx 1.31$.
    }
    \label{fig:H}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{figs/test/D_vs_eps_a.pdf}
    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $D_\alpha$ is decreasing in $\alpha$ and $\epsilon$ (\cref{thm:H2D}).
    }
    \label{fig:D}
\end{figure}

@@

Consider the partial derivatives
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
\end{equation}
We first note that for $\alpha$ in the given form, it is always true that
\begin{equation}
	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
\end{equation}
We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we then obtain the first derivative
\begin{equation}
	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
\end{equation}
because $\alpha > 1$ and
\begin{equation}
	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{1}{2b-1}}\right)^{2(a-2b+1)} \geq 0,
\end{equation}
where each expression is well-defined because the rational exponent has odd denominator.

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
\end{proof}
We note that if $\alpha =a/b$ with both $a$ and $b$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has bounded negativity then $\log \sum_{\x} W_\rho(\x)^\alpha$ can still be obtained for $a$ odd, provided the sum is never negative.

If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $f(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ is not monotonic. For example: If $\alpha = 2/3$, then $f(-2/3) = -3.43$, $f(-1/3) = -4.33$ and $f(+1/3) = +4.33$. Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.

@@

\subsection{Renyi divergences on quasi-distributions}
Now we define the classical $\alpha$-Renyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
\begin{equation}
	D_\alpha(W_\rho || W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
\end{equation}
where $\alpha$ can take values of the form $2a/(2b+1)$, for non-negative integers $a,b$ to ensure once again that the argument of the logarithm is positive.

@@

\begin{theorem}\label{thm:H2D}
	Let $\w\in \mathbb{R}^N$ be a quasi-distribution and $\r \in \mathbb{R}^N$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
	Then,
	\begin{equation}
		H_\alpha(\Gamma_{\bma}(\w)) = K - D_\alpha(\w ||\r),
	\end{equation}
	where $\alpha = 2c / (2d+1)$ for non-negative integers $c,d$ such that $H_\alpha(\x)$ is well-defined for all $\x$.
\end{theorem}
\begin{proof}
	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\x ||\r)$ is well-defined for all $\x$.

>>>>

\begin{abstract}
Magic states are key ingredients in schemes to realise universal fault-tolerant quantum computation.
Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms. Here we develop a statistical mechanical framework in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits. While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds. These upper bounds are shown to be tighter than other bounds, such as mana and thauma, and moreover incorporate hardware physics, such as temperature dependence and physical Hamiltonians. We also show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values. We show that the mana of a magic state is the measure of divergence of these Renyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting. This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
\end{abstract}

@@

Consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$. On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, acting on the basis states as follows,
\begin{align}
    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
\end{align}
Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$. From these we can construct a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system. Given a point $\bmx \coloneqq (x, p)$ we define a displacement operator, 
\begin{equation}\label{eq:ddef}
    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ 
\end{equation}
where the phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity. We assume going forward that $d$ is an odd prime, however the case $d=2$ can also be handled, but with some additional technical caveats~\cite{Appleby_2005}. For a composite system with composite dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
\begin{equation}\label{eq:composited}
    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
\end{equation}
where now we have
\begin{align*}
	\bmx &\coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d, \\
	&\nick{= (x_1, x_2, \dots, x_n, p_1, p_2, \dots, p_n) ?}
\end{align*}
to denote the phase space point for the composite system. 
For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\x \in \mathbb{Z}_d^{2n}$.

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{figs/R_vs_A.pdf}
    \caption{\textbf{Variation of distillation bounds with Hamiltonian.} We consider $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
    }
    \label{fig:rvsa}
\end{figure}

@@

However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot Renyi divergence $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
\begin{equation}
	D_\infty (\p \hspace{1pt}||\hspace{1pt} \r) = \log \max_i \frac{p_i}{r_i}.
\end{equation}
It is clear that this does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning, and in~\cref{app:lcst_technical}, we show that this divergence has the following properties that are derived via relative majorization.
\begin{theorem}\label{thm:Dinfty} 
	Let $\tau$ be in the interior of $\F$. Then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
\begin{enumerate}
\item $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
\item $D_\infty(W_{\rho^{\otimes 2n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
\item $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\infty(W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
\end{enumerate}
\end{theorem}

@@

The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges in a well-defined way. We can write the divergence of the entropy as 
\begin{equation}
	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}
\end{equation} 
with $\epsilon \rightarrow 0^+$ through a sequence of rational values. We now recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana:
\begin{equation}
\M(\rho) = \lim_{\epsilon \rightarrow 0^+} \epsilon H_{1-\epsilon}(W_\rho).
\end{equation}
Therefore, up to a factor $2\pi i$, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies \emph{the divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(W_\rho)$.

We also note that the Renyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.  For this, the Renyi parameter becomes a temperature term $\alpha = \frac{T_0}{T}$ where $T_0$ is a reference temperature and derivatives are considered via the limit $T \rightarrow T_0$. Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$. We can therefore speculate whether the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition [\ddd{cite}]. However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [\ddd{cite}].
\nick{Do you know what you want to cite in this paragraph?}

Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for Renyi divergences of Wigner distributions.
The $\alpha$--Renyi divergence $D_\alpha(\p||\r)$ is defined as
\begin{equation}
	D_\alpha(\p \hspace{1pt}||\hspace{1pt} \r) := \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
\end{equation}
where $\p$ can be a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ can take the same values as for $H_\alpha$.
In~\cref{app:lcst_technical}, we also show that the divergence satisfies the following.

\begin{theorem}\label{thm:Da_props} 
	Let $\tau$ be in the interior of $\F$. 
	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
\begin{enumerate}
\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
\item $D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ for any $n \in \mathbb{N}$.
\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\alpha (W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
\end{enumerate}
\end{theorem}

@@

	We have the following family of upper bounds on the magic distillation rate $R := m/n$,
	\begin{equation}
		R \leq \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution. 
\end{theorem}
For magic protocols that preserve unital maps, the above bound reduces to the simpler form
\begin{equation}
	R \leq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
\end{equation}
In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
\begin{equation}
	R \leq \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
\end{equation}
The upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
%
%\begin{figure}[t!]
%    \centering
%    \subfigure[][]{%
%    \label{fig:Ra}%
%    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
%    \subfigure[][]{%
%    \label{fig:RaDiff}%
%    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
%    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation for unital protocols
%    \nick{Can compare thauma and mana for other magic states now more easily}}
%    \label{fig:rate_a_contour}
%\end{figure}

@@

We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system. Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit. It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}] \nick{and here?}. This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply. That said, for special states such as the Strange state, the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible. In~\cref{app:lcsu_technical} and~\cref{app:lcst_technical} we give additional results that may be of use for later work.

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{figs/H_vs_eps_a.pdf}
    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $H_\alpha$ is increasing in $\alpha$ and $\epsilon$. First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$. Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ that implies $6^\alpha - 2^{\alpha} = 8$, with the approximate solution $\alpha \approx 1.31$.
    }
    \label{fig:H}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{figs/D_vs_eps_a.pdf}
    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $D_\alpha$ is decreasing in $\alpha$ and $\epsilon$ (\cref{thm:H2D}).
    }
    \label{fig:D}
\end{figure}

@@

Consider the partial derivatives
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}\left( -w_i^{\alpha-1} \right).
\end{equation}
We first note that for $\alpha$ in the given form, it is always true that
\begin{equation}
	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
\end{equation}
We then show that for $\alpha$ in the given form, the function $f(w) := -w^{\alpha - 1}$ is non-increasing.
To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we can obtain the first derivative
\begin{equation}
	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
\end{equation}
because $\alpha > 1$ and
\begin{equation}
	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{a-2b+1}{2b-1}}\right)^{2} \geq 0,
\end{equation}
where each expression is well-defined because the rational exponent has odd denominator.

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
\end{proof}
We note that if $\alpha =a/b$ with both $a$ and $b$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has a sufficiently bounded negativity, then $\log \sum_{\x} W_\rho(\x)^\alpha$ can still be obtained for $a$ odd, provided the sum is never negative.

If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $f(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ is not monotonic. For example, if $\alpha = 2/3$, then $f(-2/6) = -4.33$, $f(-1/6) = -5.45$ and $f(+2/6) = +4.33$. Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.

@@

\subsection{Renyi divergences on quasi-distributions}
Now we define the classical $\alpha$-Renyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
\begin{equation}
	D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
\end{equation}
where $\alpha$ can take values of the form $2a/(2b+1)$, for non-negative integers $a,b$ to ensure once again that the argument of the logarithm is positive.

@@

\begin{theorem}\label{thm:H2D}
	Let $\w\in \mathbb{R}^N$ be a quasi-distribution and $\r \in \mathbb{R}^N$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
	Then,
	\begin{equation}
		H_\alpha(\Gamma_{\bma}(\w)) = K - D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r),
	\end{equation}
	where $\alpha = 2c / (2d+1)$ for non-negative integers $c,d$ such that $H_\alpha(\x)$ is well-defined for all $\x$.
\end{theorem}
\begin{proof}
	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\x \hspace{1pt}||\hspace{1pt} \r)$ is well-defined for all $\x$.
